Precise Data Flow Analysis\\in the Presence of Correlated Method Calls

### 2014-12-15 content/impl.tex
proof for lemma 3
minor fix

In the correlated-calls transformation lattice $\lcc$, a map that maps any receiver
to the empty set of possible types means that the corresponding data flow path is
infeasible. Therefore, a result $\rho=\resultIDE(\transCC S(P))$ of the correlated-calls IDE analysis is
converted to an IFDS result as follows:
\begin{equation}\label{eq:transCcDef}
  \backCC(\rho) = \lambda n.\{d\mid\forall r\in S\,.\,\rho(n)(d)\neq\top_T\}.
\end{equation}

@@

The meet of two micro-function representations is defined as follows:
$\setpair{I}{U} \sqcap \setpair{I'}{U'} = \setpair{\lambda r\,.\,I(r) \cup I'(r)}{\lambda r\,.\,U(r) \cup U'(r)}$.
The following lemma shows that this implementation corresponds to the meet
of the denoted functions:
\begin{lemma}\label{lem:equalMeet}
    For any pair of micro-function representations $\setpair{I}{U}$, $\setpair{I'}{U'}$,
    \[
        \denote{\setpair{I}{U} \sqcap \setpair{I'}{U'}}
        = 
        \denote{\setpair{I}{U}} \sqcap \denote{\setpair{I'}{U'}}.
    \]
\end{lemma}
\otodo{Prove this lemma in the appendix. The parts of the proof can be found in section 5.}

>>>>

In the correlated-calls transformation lattice $\lcc$, a map that maps any receiver
to the empty set of possible types means that the corresponding data flow path is
infeasible. Therefore, a result $\rho=\resultIDE(\transCC _S(P))$ of the correlated-calls IDE analysis is
converted to an IFDS result as follows:
\begin{equation}\label{eq:transCcDef}
  \backCC(\rho) = \lambda n.\{d\mid\forall r\in S\,.\,\rho(n)(d)\neq\top_T\}.
\end{equation}

@@

The meet of two micro-function representations is defined as follows:
$\setpair{I}{U} \sqcap \setpair{I'}{U'} = \setpair{\lambda r\,.\,I(r) \cup I'(r)}{\lambda r\,.\,U(r) \cup U'(r)}$.
The following lemma shows that this implementation corresponds to the meet
of the denoted functions:
\begin{lemma}\label{lem:equalMeet}
    For any pair of micro-function representations $\setpair{I}{U}$, $\setpair{I'}{U'}$,
    \[
        \denote{\setpair{I}{U} \sqcap \setpair{I'}{U'}}
        = 
        \denote{\setpair{I}{U}} \sqcap \denote{\setpair{I'}{U'}},
    \]
    where
    $\denote{\setpair{I}{U}} \sqcap \denote{\setpair{I'}{U'}}
     =\lambda m.\lambda r.\denote{\setpair{I}{U}}(m)(r)\cup\denote{\setpair{I'}{U'}}(m)(r)$.\mtodo{I added the definition of the meet of two functions.}
\end{lemma}
\otodo{Prove this lemma in the appendix. The parts of the proof can be found in section 5.}
